One more attempt on ArXe

### 2015-11-02 exp_results.tex

>>>>

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_icd_12.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. Spectra were recorded with a photon energy of $h\nu = 32$~eV. Black symbols with error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. For comparison, all spectra are shown area-normalized. 
}
 \label{figure:icd_12}
\end{figure}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_icd_l.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ for clusters of the same size, but from gas mixtures with different Xe concentration. See Figure \protect\ref{figure:icd_12} for details.
}
 \label{figure:icd_l}
\end{figure}

### 2015-11-02 theo_results.tex

\section{Theoretical Results}
%
%
\begin{table}[h]
\centering
\caption{Properties of simulated clusters.
{\it Q: Einheit von $\Gamma$? 
Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10${-6}$ aufzuschreiben, und diesen wegzulassen. 
Es w\"urde dadurch sehr viel \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.}
}
\begin{tabular}{lrrrccc}
\toprule
name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
\midrule
ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
\midrule
XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
\bottomrule
\end{tabular}
\label{table:theo_gammas}
\end{table}
%
The geometrical properties as well as the total ICD and ETMD decay widths
of the investigated structures are shown in Table \ref{table:theo_gammas}.
It is important to remember that the first ICD channel opens at a
channel opening distance of \unit[7.58]{\AA}. Therefore, in small
clusters, in which none of the possible Ar-Xe pair distances is larger than
these \unit[7.58]{\AA}, no ICD can take place. Also, by definition two xenon atoms are
required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
%Because secondary electrons are observed in the experimental spectra
%we exclude all structures without any signal from our further
%discussions.
%
%In the investigated structures several different aspects have to be
%taken into account which we will discuss separately if possible
%on selected structures.

@@

Firstly, we consider two different argon core sizes one consisting
of 13 and one consisting of 55 atoms with one xenon atom on one of
the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
for the 55 atom core). The simulated secondary electron spectra are
shown in Figure \ref{figure:surf} Panel 1.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/surf.pdf}\\
 \includegraphics[width=8.2cm]{pics/R_comp.pdf}
 \caption{Panel 1: Simulated electron-electron coincidence spectra
          for argon clusters
          consisting of 13 and 55 atoms with on additional xenon atom residing
          on top of one of the argon surfaces.\\
          Panel 2: Distribution of Ar-Xe distances $d$ in the studied ArXe
          clusters. The ICD channels open at \unit[7.58]{\AA} and
          \unit[36.00]{\AA}, respectively. Hence only pairs at longer interatomic
          distances than the gray line contribute to the coincidence spectra.
          The distance distribution of the larger cluster contains larger
          distances which correspond to peaks at higher kinetic energies of
          the ICD electron in the coincidence spectra (Panel 1).}
 \label{figure:surf}
\end{figure}

Because the structures have only one xenon atom ETMD(3) is not possible and
ICD only is to be expected. Both spectra show several smaller peaks which
are convoluted into one single peak with a maximum at
approximately \unit[0.2]{eV}. In comparison to the 13 argon atoms core
spectrum the 55 argon atoms core spectrum shows
signals at higher energies of the secondary electron. These features
can be explained by analysis of the Ar-Xe distances in the clusters shown
in Figure \ref{figure:surf} Panel 2. Every different atom pair distance
yields in a different energy of the secondary electron and only pairs
with a distance of larger than the channel opening distance
(dashed, gray line) will contribute
to the spectrum. The larger the interatomic distance is, the higher is the
kinetic energy of the secondary electron for a given channel.
Since the 55 argon atom core cluster is larger and therefore
has Ar-Xe pairs with larger distances its spectrum has signals at higher
energies as well.
This effect holds for all clusters.

For clusters with more than one xenon atom the ETMD(3) channel is possible
as well. Depending on the positions of the relative positions of the xenon
atoms in or on the cluster the spectra are expected to be different.
As an example we therefore discuss the secondary electron spectra of the
clusters with an 13 argon atoms core and two xenon atoms on different
surfaces illustrated in Figure \ref{figure:cluster_2_overview} shown in Figure
\ref{figure:2tops}. In these the xenon content is \unit[13.3]{\%} and therefore
close to the experimental ones of \unit[10-12]{\%} for the low xenon pressure.

@@

In all three cases both ICD and ETMD(3) are energetically allowed and the ICD
spectra are either identical or at least very similar consisting of one
convoluted peak at approximately \unit[0.2]{eV}. However, the ETMD(3) spectra
are very sensitive to the relative positioning of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peak due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the different decay widths decreasing with $\frac{1}{R^6}$
between the electron transfer unit and the finally ionized xenon atom.
The larger the distance between the xenon atoms is, the lower are the energies
of the secondary electrons and the higher are the decay widths. Therefore a
significant contribution from the ETMD(3) compared to the ICD is only
to be seen in case of the two xenon atoms residing on two adjacent
surfaces. The threefold peak structure of the ETMD(3) peak does in contrast to
the ICD spectrum not stem from different triple structures but from the
four different decay channels for one triple structure.

For the 55 atoms clusters the xenon content of \unit[10--12]{\%}
corresponds to six xenon atoms out of the 55 total atoms. These can have
different relative positions in the cluster. They could either be grouped
together in one part of the cluster or be evenly distributed in the cluster
as shown in Figure \ref{figure:cluster_3_overview} Panels b) and c). Their
ICD and ETMD(3) spectra are shown in Figure \ref{figure:ar_3_6in}.

>>>>

\section{Theoretical Results}
%
%
\begin{table}[h]
\centering
\caption{Properties of simulated clusters.
{\it Q: Einheit von $\Gamma$? 
Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10${-6}$ aufzuschreiben, und diesen wegzulassen. 
Es w\"urde dadurch sehr viel \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.}
}
\begin{tabular}{lrrrccc}
\toprule
name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
\midrule
ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
\midrule
XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
\bottomrule
\end{tabular}
\label{table:theo_gammas}
\end{table}
%
The geometrical properties as well as the total ICD and ETMD decay widths
of the investigated structures are shown in Table \ref{table:theo_gammas}.
It is important to remember that the first ICD channel opens at a
channel opening distance of \unit[7.58]{\AA}. In small
clusters, are Ar-Xe pair distances are below that value, therefore 
no ICD can take place. Also, by definition two Xe atoms are
required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
%Because secondary electrons are observed in the experimental spectra
%we exclude all structures without any signal from our further
%discussions.
%
%In the investigated structures several different aspects have to be
%taken into account which we will discuss separately if possible
%on selected structures.

@@

Firstly, we consider cluster having an argon core of 13 and 55 atoms with a single xenon
atom on one of the surfaces (see Figure \ref{figure:cluster_3_overview}a
for the 55 atom core).
Secondary electron spectra simulated for these systems are shown in Figure \ref{figure:surf}, top panel.
%two different argon core sizes one consisting
%of 13 and one consisting of 55 atoms with one xenon atom on one of
%the surfaces (see Figure \ref{figure:cluster_3_overview} Panel a)
%for the 55 atom core). The simulated secondary electron spectra are
%shown in Figure \ref{figure:surf} Panel 1.

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/surf.pdf}\\
 \includegraphics[width=8.2cm]{pics/R_comp.pdf}
 \caption{
 {\it Q: Generell f\"ande ich es gut wenn man die panels immer mit a), b), \dots kennzeichnen k\"onnte.}
 %
 Top panel: Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters
          consisting of 13 and 55 atoms, with an additional xenon atom residing
          on top of one of the argon surfaces.
          Bottom panel: Distribution of Ar-Xe distances $d$ in the studied ArXe
          clusters. The ICD channels to final states involving Xe 5p$_{3/2}^{-1}$ and 
          5p$_{1/2}^{-1}$ vacancies open at \unit[7.58]{\AA} and
          \unit[36.00]{\AA}, resp.; the former distance is marked by a vertical dotted line. 
          Only pairs at longer interatomic
          distances contribute to the electron emission spectra.
          Larger Ar-Xe distances, as found in the larger cluster,
          correspond to features at higher kinetic energies of
          the ICD electron (top panel).}
 \label{figure:surf}
\end{figure}

Because the structures have only one xenon atom, ETMD(3) is not possible
and only ICD is expected. 
{\it Q: What about ETMD(2)? Probably it is not important anywhere in the paper?!
Maybe we should make a general statement about this somewhere early in the discussion.}
%Both spectra show several smaller peaks which
%are convoluted into one single peak with a maximum at
%approximately \unit[0.2]{eV}. 
%In comparison to the 13 argon atoms core
%spectrum t
The spectrum pertaining to the clusters with larger (55 atom) Ar core shows
signals at higher energies of the secondary electron. These features
can be explained by looking at the Ar-Xe distances in the clusters, shown
in the bottom panel of Figure \ref{figure:surf}. 
%Every different atom pair distance
%yields in a different energy of the secondary electron and only pairs
%with a distance of larger than the channel opening distance
%(dashed, gray line) will contribute
%to the spectrum. 
In our model, there is a one-to-one correspondence between interatomic distance $d$ and kinetic energy of the ICD electron.
The larger the interatomic distance, the higher is the
kinetic energy of the secondary electron for a given channel.
%Since the 55 argon atom core cluster is larger and therefore
%has Ar-Xe pairs with larger distances its spectrum has signals at higher
%energies as well.
%This effect holds for all clusters.
This explains why the ICD spectrum for larger clusters extends to higher energies, and holds for all cluster structures.

For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon
atoms in or on the cluster, the spectra are expected to be different.
As an example, we discuss the secondary electron spectra of 
clusters with a core of 13 argon atoms and two xenon atoms on different
surfaces. The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, 
simulated spectra are shown in Figure
\ref{figure:2tops}. Their xenon content is \unit[13.3]{\%} and thus
close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.

@@

In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peak due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the lower are the energies
of the secondary electrons and the smaller are the decay widths. 
{\it Q: war: `the higher are the decay widths', falschrum, oder?}
Therefore a
significant contribution from the ETMD(3) compared to the ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The threefold peak structure of the ETMD(3) peak does in contrast to
the ICD spectrum not stem from different triple structures but from the
four different decay channels for one triple structure.

For the 55 atom clusters, a xenon content of \unit[10--12]{\%}
corresponds to six xenon atoms out of a total of 55 atoms. These can have
different relative positions in the cluster. They can either form a connected 
group in one part of the cluster or can be evenly distributed in the cluster,
as shown in Figures \ref{figure:cluster_3_overview}b and \ref{figure:cluster_3_overview}c. The
ICD and ETMD(3) spectra for these structures are shown in Figure \ref{figure:ar_3_6in}.
